---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# ggcute

<!-- badges: start -->
<!-- badges: end -->

A collection of cute things to use with ggplot2. 
Right now `ggcute` only consists of one thing: a ggplot2 port of [https://twitter.com/sailorhg](sailorhg)'s [https://sailorhg.github.io/fairyfloss/](fairyfloss) text editor theme.

## Installation

You can install ggcute from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("sharlagelfand/ggcute")
```

# theme_fairyfloss()

`theme_fairyfloss()` is a theme based off of  [https://twitter.com/sailorhg](sailorhg)'s [https://sailorhg.github.io/fairyfloss/](fairyfloss) text editor theme.

You can use it like any other ggplot2 theme:

```{r}
library(ggplot2)
library(ggcute)

ggplot(nintendo_sales, aes(x = sales_million, y = console)) +
  geom_col() +
  facet_wrap(~sales_type) + 
  theme_fairyfloss()

ggplot(nintendo_sales, aes(x = sales_million, y = console, fill = sales_type)) +
  geom_col(position = position_dodge2(width = 0.1), alpha = 0.75) +
  labs(
    x = "Sales (million)", y = "Console", title = "Nintendo sales by console",
    subtitle = "As of December 31, 2019"
  ) +
  theme(legend.title = element_blank()) +
  theme_fairyfloss()
```

It's probably (definitely) not a complete theme but at least it's cute `r emo::ji("cloud")`

`ggcute` comes with one data set built in, Nintendo sales as of December 31, 2019:

```{r}
nintendo_sales
```
