---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  dpi = 300
)
```

# ggcute

<!-- badges: start -->
<!-- badges: end -->

A collection of cute things to use with ggplot2. 

## Installation

You can install ggcute from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("sharlagelfand/ggcute")
```

## fairyfloss

`theme_fairyfloss()` is a theme based off of  [sailorhg](https://twitter.com/sailorhg)'s [fairyfloss](https://sailorhg.github.io/fairyfloss/) text editor theme.

You can use it like any other ggplot2 theme:

```{r}
library(ggplot2)
library(ggcute)

ggplot(nintendo_sales, aes(x = sales_million, y = console)) +
  geom_col() +
  facet_wrap(~sales_type) + 
  theme_fairyfloss()
```

It's probably (definitely) not a complete theme but at least it's cute `r emo::ji("cloud")`

There is a colour palette built in:

```{r}
library(scales)

show_col(ggcute:::fairyfloss_colours)
```

You can use it in plots via `scale_fill_fairyfloss()`:

```{r}
ggplot(nintendo_sales, aes(x = sales_million, y = console, fill = sales_type)) +
  geom_col(position = position_dodge2(width = 0.1), alpha = 0.75) +
  labs(
    x = "Sales (million)", y = "Console", title = "Nintendo sales by console",
    subtitle = "As of December 31, 2019"
  ) +
  scale_fill_fairyfloss() + 
  theme_fairyfloss()
```

or `scale_colour_fairyfloss()` ("color" instead of colour works too):

```{r}
ggplot(nintendo_sales, aes(x = sales_type, y = sales_million, colour = console)) + 
  geom_jitter(size = 5, alpha = 0.5) + 
  scale_colour_fairyfloss() + 
  theme_fairyfloss(base_size = 12) + 
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

Of course, you can use the palette without the theme and it's still extremely cute:

```{r}
ggplot(head(diamonds, 1000), aes(x = cut, y = carat, colour = carat)) + 
  geom_jitter() + 
  scale_colour_fairyfloss(discrete = FALSE) + 
  theme_minimal()
```

## sugarpilll

`theme_sugarpill()` is a theme based off the [Sugarpill](https://www.instagram.com/sugarpill/) [Fun Size eyeshadow palette](https://sugarpill.com/products/fun-size-palette). Similar to fairyfloss, there are also `scale_*_sugarpill()` functions.

```{r}
library(dplyr)
library(forcats)

nintendo_sales %>%
  mutate(console = fct_lump_n(console, n = 8, w = sales_million, other_level = "Other Consoles")) %>%
  group_by(console, sales_type) %>%
  summarise(sales_million = sum(sales_million)) %>%
  ungroup() %>%
  ggplot(aes(x = sales_type, y = sales_million, fill = console)) + 
  geom_col(position = position_dodge2()) + 
  facet_wrap(vars(console)) + 
  labs(x = "", y = "", title = "Nintendo units sold (millions) by console", subtitle = "Data as of December 31, 2019") + 
  scale_fill_sugarpill() + 
  theme_sugarpill() + 
  theme(legend.position = "none")
```

## Data

`ggcute` comes with one data set built in, Nintendo sales as of December 31, 2019:

```{r}
nintendo_sales
```
